AXON. A Database for Greek Historical Inscriptions.

### 2016-02-09 source/21/EAGLE2016_Full_Paper_revised.tex
axon corrections done

%%%%%%%%
%TITLE:%
%%%%%%%%
\title{AXON. A Selection of Greek Historical Inscriptions. A Database for Research and Teaching}
\author[cafo]{Stefania De Vido}
 \author[cafo]{Ivan Matijašić\corref{first}}
\author[cafo]{Silvia Palazzo}
\address[cafo]{Dipartimento di Studi Umanistici, Università Ca' Foscari Venezia}
\cortext[first]{Corresponding author. Email: ivan.matijasic@unive.it}
\begin{document}

@@

\noindent \emph{AXON. A Selection of Greek Historical Inscriptions} is a project conceived within the Greek Epigraphy Laboratory
(Director, Prof. Claudia Antonetti), and has been brought into existence with the financial support of the University
Ca’ Foscari of Venice (University Project 2013, Project Coordinator, Prof. Stefania De Vido).

@@

\begin{figure}[!bp]
\centering
 \includegraphics[width=\columnwidth]{EAGLE2016FullPaperrevised-img001.png}
\caption{Window for the input of data, section Text/Chronology}
\label{fig:1}
\end{figure}

@@

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{EAGLE2016FullPaperrevised-img002.png}
\caption{Example of Abstract in AXON. The different colours allow a selection of words from a drop-down menu. }
\label{fig:2}
\end{figure}

@@

Our aim is to establish a growing community of experts, students, and enthusiasts to increase the number of contributors
through lists of inscriptions which have not yet been assigned. At the same time it will be the possible to suggest
other texts which are not included in the lists. To achieve these aims, the project follows an EpiDoc-friendly
structure and is compatible with Europeana EAGLE Project, especially in the use of a common terminology.

@@

\begin{figure}[!bp]
\centering
 \includegraphics[width=\columnwidth]{EAGLE2016FullPaperrevised-img003.png}
\caption{Search based on ``Full text'', number, title, and author of the entry.}
\label{fig:3}
\end{figure}

\begin{enumerate}
\item browse all the entries according to the inscriptions’ a) typology, b) chronology, and c) area of origin;
\item access the entries through an interactive map;
\item perform an advanced search based on different categories: 
\begin{enumerate}
\item bibliography
\item keywords
\item object’s description and preservation (see Fig.~\ref{fig:4})
\item chronology
\item text (single words or phrases, typology, dialect, alphabet, letter-form, etc.) (see Fig.~\ref{fig:5}).
\end{enumerate}
\end{enumerate}

\begin{figure}[!bp]
\centering
 \includegraphics[width=\columnwidth]{EAGLE2016FullPaperrevised-img004.png}
\caption{Different searching categories.}
\label{fig:4}
\end{figure}

\begin{figure}[!bp]
\centering
 \includegraphics[width=\columnwidth]{EAGLE2016FullPaperrevised-img005.png}
\caption{Advanced text search}
\label{fig:5}
\end{figure}

Other filters will be employed for each search result. A section entitled ``tools'' will also be available, and will
include information on the entries’ structure, tables with the contents of different categories, links to Vocabularies
and websites, etc.

>>>>

%%%%%%%%
%TITLE:%
%%%%%%%%
\title{AXON. A Database for Greek Historical Inscriptions.}
\author[cafo]{Stefania De Vido}
 \author[cafo]{Ivan Matijašić\corref{first}}
\author[cafo]{Silvia Palazzo}
\address[cafo]{Dipartimento di Studi Umanistici, Università Ca' Foscari Venezia}
\cortext[first]{Corresponding author. Email: ivan.matijasic@unive.it}
\begin{document}

@@

\noindent \emph{AXON. A Selection of Greek Historical Inscriptions} is a project conceived within the Greek Epigraphy Lab (Director, Prof. Claudia Antonetti), and has been brought into existence with the financial support of the University
Ca’ Foscari of Venice (University Project 2013, Project Coordinator, Prof. Stefania De Vido; Scientific Team: Ivan Matijašić, Silvia Palazzo, Michela Socal, Luigi Tessarolo [IT Project]).

@@

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{Fig1.png}
\caption{Window for the input of data, section Text/Chronology}
\label{fig:1}
\end{figure}

@@

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{Fig2.png}
\caption{Example of Abstract in AXON. The different colours allow a selection of words from a drop-down menu. }
\label{fig:2}
\end{figure}

@@

Our aim is to establish a growing community of experts, students, and enthusiasts to increase the number of contributors
through lists of inscriptions which have not yet been assigned. At the same time it will be possible to suggest
other texts which are not included in the lists. To achieve these aims, the project follows an EpiDoc-friendly
structure and is compatible with Europeana EAGLE Project, especially in the use of a common terminology.

@@

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{EAGLE2016FullPaperrevised-img003.png}
\caption{Search based on ``Full text'', number, title, and author of the entry.}
\label{fig:3}
\end{figure}

\begin{enumerate}
\renewcommand{\theenumi}{\alph{enumi}}
\item browse all the entries according to the inscriptions’ a) typology, b) chronology, and c) area of origin;
\item access the entries through an interactive map;
\item perform an advanced search based on different categories: 
\begin{enumerate}
\renewcommand{\theenumi}{\alph{enumi}}
\item bibliography
\item keywords
\item object’s description and preservation (see Fig.~\ref{fig:4})
\item chronology
\item text (single words or phrases, typology, dialect, alphabet, letter-form, etc.) (see Fig.~\ref{fig:5}).
\end{enumerate}
\end{enumerate}

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{EAGLE2016FullPaperrevised-img004.png}
\caption{Different searching categories.}
\label{fig:4}
\end{figure}

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{EAGLE2016FullPaperrevised-img005.png}
\caption{Advanced text search}
\label{fig:5}
\end{figure}

Other filters will be employed for each search result. A section entitled ``tools'' is also available, and it
includes information on the entries’ structure, tables with the contents of different categories, links to Vocabularies
and websites, etc.
